The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-01-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated tables 1 and 4, Figure 2

  \subsubsection{Averaging matched photometry}
  The data was processed using a matched-aperture photometry method
  where flux is measured at the spectroscopic position of the quasar,
  without necessarily knowing if there is a formal detection in the NIR
  photometry beforehand. The matched-aperture pipeline is discussed in
  \citet{Cross2013} and with fuller details to appear in a forthcoming
  paper (Cross et al., 2019, in prep).

@@

\begin{table}
  \centering
  \begin{tabular}{l r l}
    \hline  \hline
    Selection   & number detected (\%) \\
    \hline  
    Any band ($ZYJHK/K_{s}$)    &  473  (96.9) \\
    $Z$-band                            &  81  (16.5) \\
    $Y$-band                            &  289  (59.2) \\
    $J$-band                              &  471  (96.5) \\
    $H$-band                            &  277  (56.8) \\
    $K$ or $Ks$-band                &  343  (70.2) \\
    \hline  \hline
  \end{tabular}
  \caption{Detection rate of VH$z$Qs in the near-infrared. 
For the 14 objects that have no NIR detections, 3 have 
been observed but are not in our queried time range, 6 have 
not been observed yet and 5 objects are too far north to be visible 
by UKIRT. }
  \label{tab:nir_detection}
\end{table}

@@

  \subsubsection{Comparing WFCAM and VISTA}
  There are 131 quasars observed in the overlapping area between WFCAM
  and VISTA. We used the {\tt VegaToAB} values to put these objects on
  the same AB system, and for each object compared the two
  measurements. First, we calculated the weighted average (calibrated
  flux) in each filter of both and calculated the ratio and difference
  between each measurement and the average.  Then for each filter we
  calculated the weighted average of the differences (in mag) for each
  instrument to see if there were significant offsets. The results are
  given in Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a
  significant offset is the $Y$-band. All of the VISTA averages are
  negative and all of the WFCAM ones are positive. The $Ks$ versus $K$
  band comparison may be affected the different shapes of the filters,
  with $K$ being significantly wider than $K_s$, able to detect light at
  longer wavelengths.
  \begin{table}
    \centering
    \begin{tabular}{l r r}
      \hline  \hline
      abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
      -  WFCAM)      &                                        &  objects \\
      \hline
      $Z$                 &  7.2 	& 3 \\
      $Y$                 &  59.1 	& 62 \\
      $J$                  &    6.3 	& 111 \\
      $H$                 &  41.7     &  103 \\
      $K_{\rm s}$/$K$ &  15.1     & 114 \\
      \hline  \hline
    \end{tabular}
    \caption{Comparing the magnitudes in different WFCAM/UKIRT and 
      VIRCAM/VISTA near-infrared bands.}
    \label{tab:WFCAM_vs_VISTA}
  \end{table}

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with
  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
  were removed. This selects one quasar with large, $\delta$mag
  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
  which has a WSA $K$-band magnitude of 21.03$\pm$0.35 AB (observed at
  MJD=54062.4), while for the VSA $K_s$-band this is 20.21$\pm$0.14 mag AB
  (observed 3 times between MJD=55537 and 55542). The WFCAM and VISTA
  observations are $\sim4$ years apart.

>>>>

  \subsubsection{Averaging matched photometry}
  The data was processed using a matched-aperture photometry method
  where flux is measured at the spectroscopic position of the quasar,
  without necessarily knowing if there is a formal detection in the NIR
  photometry beforehand. The matched-aperture pipeline is discussed in
  \citet{Cross2013} and with fuller details to appear in a forthcoming
  paper (Cross et al., 2020, in prep).

@@

\begin{table}
  \centering
  \begin{tabular}{l r l}
    \hline  \hline
    Selection   & number detected (\%) \\
    \hline  
    Any band ($ZYJHK/K_{s}$)    &  473  (96.9) \\
    $Z$-band                            &  81  (16.6) \\
    $Y$-band                            &  289  (59.2) \\
    $J$-band                              &  471  (96.5) \\
    $H$-band                            &  277  (56.8) \\
    $K$ or $Ks$-band                &  343  (70.3) \\
    \hline  \hline
  \end{tabular}
  \caption{Detection rate of VH$z$Qs in the near-infrared. 
For the 15 objects that have no NIR detections, 3 have 
been observed but are not in our queried time range, 6 have 
not been observed yet and 6 objects are too far north to be visible 
by UKIRT. }
  \label{tab:nir_detection}
\end{table}

@@

  \subsubsection{Comparing WFCAM and VISTA}
  There are 131 quasars observed in the overlapping area between WFCAM
  and VISTA. We used the {\tt VegaToAB} values to put these objects on
  the same AB system, and for each object compared the two
  measurements. First, we calculated the weighted average (calibrated
  flux) in each filter of both and calculated the ratio and difference
  between each measurement and the average.  Then for each filter we
  calculated the weighted average of the differences (in mag) for each
  instrument to see if there were significant offsets. The results are
  given in Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a
  significant offset is the $Y$-band. All of the VISTA averages are
  negative and all of the WFCAM ones are positive. The $K_s$ versus $K$
  band comparison may be affected the different shapes of the filters,
  with $K$ being significantly wider than $K_s$, able to detect light at
  longer wavelengths.
  \begin{table}
    \centering
    \begin{tabular}{l r r}
      \hline  \hline
      abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
      -  WFCAM)      &                                        &  objects \\
      \hline
      $Z$                 &  7.2 	& 3 \\
      $Y$                 &  59.1 	& 62 \\
      $J$                  &    6.3 	& 111 \\
      $H$                 &  41.7     &  103 \\
      $K_{\rm s}$/$K$ &  15.1     & 114 \\
      \hline  \hline
    \end{tabular}
    \caption{Comparing the magnitudes in different WFCAM/UKIRT and 
      VIRCAM/VISTA near-infrared bands.}
    \label{tab:WFCAM_vs_VISTA}
  \end{table}

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with
  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
  were removed. This selects one quasar with large, $\delta$mag
  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
  which has a WSA $K$-band magnitude of 21.03$\pm$0.35 mag AB (observed at
  MJD=54062.4), while for the VSA $K_s$-band this is 20.21$\pm$0.14 mag AB
  (observed 3 times between MJD=55537 and 55542), meaning that the WFCAM and
  VISTA observations are $\sim4$ years apart.
